\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-05-25 paper/paper.tex
Updated plots

\begin{figure}
\includegraphics[width=\textwidth]{fig/heterogeneity_compare_preliminary.pdf}
\caption{Left: Kaplan-Meier estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median time to failure curves for Models 1-4, orderered left to right, top to bottom.}
\label{fig2}
\end{figure}

@@

\subsection{Model Comparisons}
The right side of Figure \ref{fig2} shows that the set of estimated failure curves for all four models that we fit. The upper left panel shows the estimated failure curve fit to all data ignoring drive model as a factor (Model 1). The upper left plot, which represents Model 2, demonstrates that there is appreciable differentiation between drive models; note that, since the scale parameter, $\tau_{t_{p2}}$ is learned hierarchically from the data, we can ascertain that there is evidence in the data that this variability is real.

>>>>

\begin{figure}
\includegraphics[width=.8\textwidth]{fig/data_overview}
\caption{Left: Kaplan-Meier plots showing nonparametric estimates of fraction failing for individual drive-models with truncation adjustments based on fitted model, Right: Total observed failures (top) and the sum of lengths of all observational intervals by drive-model.}
\end{figure}

@@

\subsection{Model Comparisons}
\begin{figure}
\includegraphics[width=\textwidth]{fig/heterogeneity_compare_preliminary.pdf}
\caption{Left: Kaplan-Meier estimates of the time to failure for each of the drive-models in the Backblaze data. Right: Pointwise posterior median time to failure curves for Models 1-4, orderered left to right, top to bottom.}
\label{fig2}
\end{figure}

The right side of Figure \ref{fig2} shows that the set of estimated failure curves for all four models that we fit. The upper left panel shows the estimated failure curve fit to all data ignoring drive model as a factor (Model 1). The upper left plot, which represents Model 2, demonstrates that there is appreciable differentiation between drive models; note that, since the scale parameter, $\tau_{t_{p2}}$ is learned hierarchically from the data, we can ascertain that there is evidence in the data that this variability is real.
